Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-07 sections/01-introduction.tex
Update on Overleaf.

>>>>

 While the introduction of new medical measurement methods requires a comprehensive evaluation and comparison with established standard measurement methods to ensure their validity and reliability, it is generally important for forecasts and nowcasting methods to assess the extent to which the predictions correspond to the development of reality.
